Chatbots in the classroom: an analysis from the teacher's perspective

### 2021-05-21 edubots_surveys.Rnw
Describes the population sample

% Describe the survey and population
We collected responses from a total of XXX teachers from University and Vocational Education from Spain ...

>>>>

% Describe the survey and population
We collected responses from a 282 teachers from Spain and Spanish Speaking countries. The sample includes teachers from university (68\%) and vocational Education (32\%). Regarding gender, 63\% are male teachers and 35\% female (approximately 2\% chose not to disclose it). Finally, the responses are equally distributed attending to the teaching experience, showing 24\% of responses from teachers with 5 or less years of experience, 27\% for 6-15 years of experience, 30\% for 16-25, and 19\% for teachers with more than 25 years of experience.
